### 2019-10-04 paper/paper.tex
Adds some potential subsection titles for the results section.

@@

\subsection*{Basic results}

@@

\subsection*{With surrounding large domains}

Maybe, put this in to remind myself that I did this. It looks nice.

\subsection*{Plucking experiments}

Include results of plucking a single whisker, a row of whiskers and a
column of whiskers.

\subsection*{Any parameter sweeps necessary to show behaviour is
  robust to changes in params}

Go here.

\subsection*{Manipulating Competition: Group competition stronger/weaker than inter-group competition}

@@

\subsection*{Manipulating Guidance: Relative interaction strengths}

@@

\subsection*{Manipulating Guidance: Delayed onset in one axis}

@@

\subsection*{Manipulating Guidance: Different guidance profiles}

>>>>

\usepackage{titlesec}
\titleformat*{\section}{\LARGE\bfseries}
\titleformat*{\subsection}{\Large\bfseries}
\titleformat*{\subsubsection}{\large\bfseries}
\titleformat*{\paragraph}{\large\bfseries}
\titleformat*{\subparagraph}{\large\bfseries}

@@

\subsection*{Competition is required to form somatotopically ordered barrels}

@@

\subsection*{The barrel field reacts to changes in the expression pattern of guidance molecules}

To cover the reaction to changes in the guidance molecules caused by
experiments like those by Shimogori \& Grove.

\subsection*{The barrel field reacts to simulated whisker plucking}

A section on whisker plucking?

%\subsubsection*{With surrounding large domains}
%Maybe, put this in to remind myself that I did this. It looks nice.

%\subsection*{Plucking experiments}
%Include results of plucking a single whisker, a row of whiskers and a
%column of whiskers.

%\subsection*{Any parameter sweeps necessary to show behaviour is
%  robust to changes in params}

\subsection*{Extending the model to capture row and arc development}

\subsubsection*{Manipulating Competition: Group competition stronger/weaker than inter-group competition}

@@

\subsubsection*{Manipulating Guidance: Relative interaction strengths}

@@

\subsubsection*{Manipulating Guidance: Delayed onset in one axis}

@@
